---
title: "Pre-survey Qualrics Analysis for Collaborative Problem Solving in Asymmetric Virtual Reality"
output: html_document
date: "`r Sys.Date()`"
---

# Exploring the data

This survey contains the TIPI and VGEM along with two single question measures for virtual reality usage 
and teammate familiarity. Additional details about the questions and scoring specifics can be found in the
root level README.

To begin our analysis, we will look at the columns and summary statistics to get an idea of how the data 
is saved and exported from Qualtrics.

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(lubridate) 
library(gghighlight)
library(RColorBrewer)
library(gridExtra)
library(tidyr)
library(stringr)
library(R.utils)


```

```{r}

preData <- read.csv("../HCC8500-pre_04-03.csv")
experimentData <- read.csv("../Experiment_Log.csv")

colnames(preData)
# our data starts at pid
head(preData)
# first two rows are subheadings/labels and can be removed
preData <- preData[- (1:2), ] %>%
  select(-StartDate, -EndDate, -Status, -IPAddress, -Progress, -Duration..in.seconds., -Finished, -RecordedDate, -ResponseId, -RecipientLastName, -RecipientFirstName, -RecipientEmail, -ExternalReference, -LocationLatitude, -LocationLongitude, -DistributionChannel, -UserLanguage)
head(preData)

preData$pid <- toupper(preData$pid)


summary(preData)

colnames(experimentData)
# Session.ID, VR.PID, PC.PID are the important ones for parsing data
head(experimentData)

summary(experimentData)

# add the experiment data to the make dataframe
experimentData_long <- experimentData %>%
  tidyr::pivot_longer(cols = c(VR.PID, PC.PID), 
                      names_to = "PID_Type", 
                      values_to = "pid") %>%
  select(Session.ID, pid, PID_Type, Number_of_tasks, Solar_Flares_Avoided)

preData <- preData %>%
  left_join(experimentData_long, by = "pid") 

head(preData)


```
# TIPI Scoring

Even number questions are reverse scored, and the pairs for each facet are averaged. 1 is paired with 6, 2 is paired with 7, 3 is paired with 8, 4 is paired with 9 and 5 is paired with 10.

```{r tipi}

# add columns to data frame 
preData <- preData %>%
  mutate(extraversion = (as.numeric(tipi_1) + (8 - as.numeric(tipi_6))) / 2) %>%
  mutate(agreeableness = (as.numeric(tipi_2) + (8 - as.numeric(tipi_7))) / 2) %>%
  mutate(conscientiousness = (as.numeric(tipi_3) + (8 - as.numeric(tipi_8))) / 2) %>%
  mutate(emotionalStability = (as.numeric(tipi_4) + (8 - as.numeric(tipi_9))) / 2) %>%
  mutate(openness = (as.numeric(tipi_5) + (8 - as.numeric(tipi_10))) / 2)


```


# VGEM Scoring

The scoring for VGEM is a bit convoluted. Tables explaining the scoring can be found in the main README. The measure consists of 5 factors.

```{r vgem}

# WARNING rerun entire script before using this data to avoid unwanted data manipulations

# Score the data that needs scoring
vgemData <- preData %>%
  mutate(Q1._1 = as.numeric(Q1._1) * 5 ) %>%
  mutate(Q1._2 = as.numeric(Q1._2) * 5 ) %>%
  mutate(Q1._3 = as.numeric(Q1._3) * 5 ) %>%
  mutate(Q3_1 = as.numeric(Q3_1) * (100/7) ) %>%
  mutate(Q3_2 = as.numeric(Q3_2) * (100/7) ) %>%
  mutate(Q3_3 = as.numeric(Q3_3) * (100/7) ) %>%
  mutate(Q3_4 = as.numeric(Q3_4) * (100/7) ) %>%
  mutate(Q3_5 = as.numeric(Q3_5) * (100/7) ) %>%
  mutate(Q6 = as.numeric(Q6) * 25 ) %>%
  mutate(Q7 = as.numeric(Q7) * (100/6) ) %>%
  mutate(Q10_1 = ( as.numeric(Q10_1) + 100 ) / 2 ) %>%
  mutate(Q11 = as.numeric(Q11) * (100/6) )

preData <- vgemData %>%
  mutate(skillConfidence = (as.numeric(Q9_1) + as.numeric(Q9_2) + as.numeric(Q9_3) + as.numeric(Q9_4) + as.numeric(Q9_5) + as.numeric(Q9_6) + as.numeric(Q9_7) + as.numeric(Q9_8) + as.numeric(Q10_1)) / 9) %>%
  mutate(gameLifespan = (as.numeric(Q1._1) + as.numeric(Q1._2) + as.numeric(Q1._3)) / 3 ) %>%
  mutate(gameIntensity = (as.numeric(Q3_5) + as.numeric(Q8_1) + as.numeric(Q9_2) + as.numeric(Q9_3) + as.numeric(Q11)) / 5 ) %>%
  mutate(gameFrequency = (as.numeric(Q3_2) + as.numeric(Q3_3)) / 2) %>%
  mutate(gameSelfEfficacy = (as.numeric(Q3_2) + as.numeric(Q6) + as.numeric(Q7)) / 3)



```


# Plotting team composition

To get an overview of the individual differences (Big Five & VGEM), they will be plotted corresponding to the groups.

```{r id_plots}
# VGEM
vgem_long <- preData %>%
  tidyr::pivot_longer(cols = c(skillConfidence, gameLifespan, gameIntensity, gameFrequency, gameSelfEfficacy), 
                      names_to = "VGEM_facet", 
                      values_to = "vgem") %>%
  select(Session.ID, pid, PID_Type, VGEM_facet, vgem) %>%
  mutate(PID_Type = dplyr::recode(PID_Type, PC.PID = "PC", VR.PID = "VR"))


vgem_long %>%
  ggplot(aes(x=VGEM_facet, y=vgem, group=PID_Type, fill=PID_Type)) +
  geom_bar(position="dodge", stat = "identity") +
  theme_minimal() +
  scale_fill_manual(values=met.brewer("Archambault", 2)) +
  facet_wrap(~Session.ID, ncol=4) +
  coord_flip() +
  labs(title = "Overview of Team Composition in Terms of Video Game Experience", fill="Modality Type", x="Video Game Experience Facet", y="Score out of 100")


# Big Five (TIPI)
tipi_long <- preData %>%
  tidyr::pivot_longer(cols = c(openness, conscientiousness, extraversion, agreeableness, emotionalStability), 
                      names_to = "TIPI_facet", 
                      values_to = "tipi") %>%
  select(Session.ID, pid, PID_Type, TIPI_facet, tipi) %>%
  mutate(PID_Type = dplyr::recode(PID_Type, PC.PID = "PC", VR.PID = "VR"))

tipi_long %>%
  ggplot(aes(x=TIPI_facet, y=tipi, group=PID_Type, fill=PID_Type)) +
  geom_bar(position="dodge", stat = "identity") +
  theme_minimal() +
  scale_fill_manual(values=met.brewer("Archambault", 2)) +
  facet_wrap(~Session.ID, ncol=4) +
  coord_flip() +
  labs(title = "Overview of Team Composition in Terms of Big Five Personality", fill="Modality Type", x="Big Five Facet", y="Score out of 7")

  

```

