---
title: "Pre-survey Qualrics Analysis for Collaborative Problem Solving in Asymmetric Virtual Reality"
output: html_document
date: "`r Sys.Date()`"
---

# Exploring the data

This survey contains the TIPI and VGEM along with two single question measures for virtual reality usage 
and teammate familiarity.Additional details about the questions and scoring specifics can be found in the
root level README.

To begin our analysis, we will look at the columns and summary statistics to get an idea of how the data 
is saved and exported from Qualtrics.

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(lubridate) 
library(gghighlight)
library(RColorBrewer)
library(gridExtra)
library(tidyr)
library(stringr)
library(R.utils)


```

```{r}

preData <- read.csv("../HCC8500-pre_03-18.csv")
experimentData <- read.csv("../Experiment_Log.csv")

colnames(preData)
# our data starts at pid
head(preData)
# first two rows are subheadings/labels and can be removed
preData <- preData[- (1:2), ] %>%
  select(-StartDate, -EndDate, -Status, -IPAddress, -Progress, -Duration..in.seconds., -Finished, -RecordedDate, -ResponseId, -RecipientLastName, -RecipientFirstName, -RecipientEmail, -ExternalReference, -LocationLatitude, -LocationLongitude, -DistributionChannel, -UserLanguage)
head(preData)

summary(preData)

colnames(experimentData)
# Session.ID, VR.PID, PC.PID are the important ones for parsing data
head(experimentData)

summary(experimentData)

```
# TIPI Scoring

Even number questions are reverse scored, and the pairs for each facet are averaged. 1 is paired with 6, 2 is paired with 7, 3 is paired with 8, 4 is paired with 9 and 5 is paired with 10.

```{r tipi}

# add columns to data frame 
preData <- preData %>%
  mutate(extraversion = (as.numeric(tipi_1) + (8 - as.numeric(tipi_6))) / 2) %>%
  mutate(agreeableness = (as.numeric(tipi_2) + (8 - as.numeric(tipi_7))) / 2) %>%
  mutate(conscientiousness = (as.numeric(tipi_3) + (8 - as.numeric(tipi_8))) / 2) %>%
  mutate(emotionalStability = (as.numeric(tipi_4) + (8 - as.numeric(tipi_9))) / 2) %>%
  mutate(openness = (as.numeric(tipi_5) + (8 - as.numeric(tipi_10))) / 2)

# select the columns to save to new df
tipiData <- select(preData, extraversion, agreeableness, conscientiousness, emotionalStability, openness)

# remove the columns from original df
preData <- select(preData, -extraversion, -agreeableness, -conscientiousness, -emotionalStability, -openness)

```

